---
title: "DBN: SE Data visualization"
author: "Praveen Kenderla"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    css: !expr here::here('R', 'css', 'style.css')
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(dev.args = list(type = "cairo"))

```


## Loading Libraries
```{r libraries, message=FALSE}
# 1. Checks if is a pacman library installed if not installs it
if (!requireNamespace("pacman")) install.packages("pacman")

# 2. Uploads all the libraries using pacman package
pacman::p_load(ggplot2, dplyr, purrr, tibble, tidyr, lme4, lmerTest, 
               psych, Cairo, ggh4x, gridExtra, gtable, grid, gt, here, 
               extrafont, conflicted, rlang, systemfonts)

#from here on prefers dplyr filter if there is a conflict with filter function
conflict_prefer("filter", "dplyr")

# loadfonts(device = "win")
# fonts()
```

## Anti-aliasing for windows
```{r anti-aliasing, message=FALSE, results='hide'}
# code taken from this place: https://github.com/rstudio/rstudio/issues/2142
trace(grDevices:::png, quote({
  if (missing(type) && missing(antialias)) {
    type <- "cairo-png"
    antialias <- "subpixel"
  }
}), print = FALSE)
```

## Load source files
```{r loading_source_files, message=FALSE}
# Loads the primary data cleaning script; "here" makes rproj as absolute path;
source(here("R/data_cleaning/child_se_datacleaning.R"))

# Load data viz functions;
source(here("R/functions/data_viz_function_list.R"))
```

## Table
### 1. Table data preparation
```{r table-prep, message=FALSE}
#Summary of responses: gives averages response for each category:
df_child_avg <- df_child_analysis %>%
  group_by(participant_ID, country, category, child_age_years) %>%
  summarise(avgScore = mean(response, na.rm = TRUE), n = n()) %>% 
  ungroup()
  
### Permutations without repetitions: 
# Permutations without repetition (n=3, r=3)
# Using Items: a,b,c
# List has 6 entries.
# {a,b,c} {a,c,b} {b,a,c} {b,c,a} {c,a,b} {c,b,a}
# G>R>W; G>W>R; R>G>W; 
# R>W>G; W>G>R; W>R>G;

child_avg_table <- df_child_avg %>% 
  pivot_wider(names_from = category, values_from = avgScore) %>% 
  mutate(G_R_W = case_when(
    gender > religion & religion > wealth ~ "GRW",
    gender > wealth & wealth > religion ~ "GWR",
    religion > gender & gender > wealth ~ "RGW",
    
    religion > wealth & wealth > gender ~ "RWG",
    wealth > gender & gender > religion ~ "WGR",
    wealth > religion & religion > gender ~ "WRG",
    gender == religion & religion == wealth ~ "All_equal",
    
    gender > religion & religion == wealth ~ "G>R=W",
    religion > wealth & religion == gender ~ "R>W=G",
    wealth > gender & gender == wealth ~ "W>G=G",
    TRUE ~ "Other"
  )
  ) %>% group_by(country,G_R_W) %>% 
  summarise(total = n()) %>% 
  mutate(percentage_kids = (round((total / sum(total)*100), 2))) %>%
  select(-total) %>% 
  pivot_wider(names_from = G_R_W, values_from = percentage_kids) %>% 
  mutate(total = round(sum(GRW, GWR, RGW, RWG, WGR, WRG,Other, All_equal,
                           `G>R=W`, `R>W=G`,
                           na.rm=TRUE),0)) %>% 
  relocate(c(`G>R=W`, `R>W=G`, All_equal, Other), .after=WRG) 
# relocate(All_equal, .after=WRG)
#  mutate(total_per = sum(Other, gender_over_all, religion_over_all, wealth_over_all, ## # g>r<=w, r>w<=g, na.rm=T))

child_avg_table[is.na(child_avg_table)] <- 0

#colnames(child_avg_table)
#adding this because there are no W>R=G values as of now but we still want to 
# show that in the table for clarity purpose. But change this if there are 
# any responses for the W>R=G combination!
child_avg_table  <- child_avg_table %>% 
  mutate(`W>R=G` = 0) %>% 
  relocate(`W>R=G`, .after = `R>W=G`)
  
```

### 2. Constructing table for average essentialism scores
```{r summary-table-figure, message=FALSE}
# adding percentage symbols to the data
df_child_table <- child_avg_table %>%
  mutate(across(everything(), ~ paste0(., "%"))) %>%
  ungroup() %>%
  mutate(country = as.character(country))

child_tbl <- gt(df_child_table) %>%
  tab_spanner(label = "Gender greater",
              columns = c(GRW, GWR, `G>R=W`),
              id = "S1") %>%
  tab_spanner(label = "Religion greater",
              columns = c(RGW, RWG, `R>W=G`),
              id = "S2") %>%
  tab_spanner(label = "Wealth greater",
              columns = c(WGR, WRG, `W>R=G`),
              id = "S3") %>%
  # cols_label(country = "Country") %>%
  tab_style(
    style = cell_text(
      size = "smaller",
      weight = "bold",
      transform = "uppercase"
    ),
    locations = list(cells_body(columns = country), cells_column_labels())
  ) %>%
  tab_style(
    style = cell_text(size = "smaller", weight = "bold"),
    locations = list(cells_column_spanners(everything()))
  ) %>%
  tab_style(
    style = cell_borders(
      sides = c("bottom"),
      color = "#000000",
      style = "solid",
      weight = px(2)
    ),
    locations = list(
      cells_column_labels(),
      cells_column_spanners(everything()),
      cells_body(everything())
    )
  ) %>%
  tab_style(
    style = cell_borders(
      sides = c("left", "right"),
      color = "black",
      weight = px(2)
    ),
    locations = list(cells_body(columns = 1), 
                     cells_column_labels(columns = c(country)))
  ) %>%
  tab_style(
    style = cell_borders(
      sides = c("right"),
      color = "black",
      weight = px(2)
    ),
    locations = list(cells_body(columns = total), 
                     cells_column_labels(columns = c(total)))
  ) %>%
  opt_stylize(style = 1, color = "gray") %>%
  opt_horizontal_padding(scale = 2) %>%
  cols_align(align = c("center"), columns = -country) %>%
  # cols_align(align = "left", columns = 1) %>%
  opt_vertical_padding(scale = 1) %>%
  tab_options(
    column_labels.padding = px(1),
    column_labels.background.color = "#FFEFD550",
    column_labels.font.size = px(10)
  ) %>%
  tab_header(title = "Children response patterns compared between social categories for each country", 
             subtitle = "Essentialism average percentages") %>%
  # opt_align_table_header(align = "left") %>%
  tab_options(
    heading.background.color = "#FFEFD590",
    heading.align = "left",
    heading.padding = px(10),
    heading.padding.horizontal = px(2),
    heading.title.font.size = px(18)
  ) %>%
  tab_style(style = cell_borders(
    sides = c("left", "right"),
    color = "black",
    weight = px(2)
  ),
  locations = cells_title()) %>%
  # opt_table_font(
  #   font = list(
  #     google_font(name = "Merriweather"),
  #     "Cochin", "serif"
  #   )) %>%
  tab_style(cell_text(font = list(google_font(name = "Lexend Deca"), "serif")), locations = cells_title()) %>%
  tab_style(cell_text(font = list(google_font(name = "Lexend Deca"), "serif")),
            locations = list(cells_body(), cells_column_labels())) %>%
  tab_style(cell_text(size = px(16)), locations = list(cells_column_labels()))

child_tbl %>% tab_options(table.width = "100%",
                          table.align = "center",
                          table.layout = "fixed")

#save the table----
#gtsave(b_tbl, "patterns_table.html")

```

## Plots at item level
### 1. Born item
> ***Q. "Are people born that way? Like, [OUTGROUP] are born [OUTGROUP] and [INGROUP] are born [INGROUP]? "***

```{r message=FALSE,fig.width=12, fig.height=8, fig.fullwidth = TRUE}
# These plots are according to the analysis representation 
# where we test the for each item!

# omitting NA rows:
df_child_analysis <- na.omit(df_child_analysis)

#Plot for each item----
#Born item:
born_plot <- plot_making(
  df_child_analysis,
  child_age_years,
  response,
  filter_var = (df_child_analysis$item == "born"),
  color_variable = category,
  facet_var = country,
  title_name = "BORN"
) + plot_theme(base_family = "Roboto") 

born_plot

```

### 2. Internal Item
> ***Q. "Is it possible to tell whether a person is [OUTGROUP] or [INGROUP] just by looking inside their body, like their blood and bones?"***

```{r message=FALSE,fig.width=12, fig.height=8, fig.fullwidth = TRUE}
#Internal item:
internal_plot <- plot_making(
  df_child_analysis,
  child_age_years,
  response,
  filter_var = (df_child_analysis$item == "internal"),
  color_variable = category,
  facet_var = country,
  title_name = "INTERNAL"
) + plot_theme(base_family = "Roboto")

internal_plot
```

### 3. Souls Item
> ***Q. "Are [OUTGROUP] people’s souls different from [INGROUP] people’s souls? "***

```{r message=FALSE,fig.width=12, fig.height=8, fig.fullwidth = TRUE}
#Souls item:
souls_plot <- plot_making(
  df_child_analysis,
  child_age_years,
  response,
  filter_var = (df_child_analysis$item == "souls"),
  color_variable = category,
  facet_var = country,
  title_name = "SOULS"
) + plot_theme(base_family = "Roboto")

souls_plot
```

### 4. Change Item:
> ***Q. "Is it possible for [OUTGROUP] to become [INGROUP]?"***

```{r message=FALSE,fig.width=12, fig.height=8, fig.fullwidth = TRUE}
#Change item:
change_plot <- plot_making(
  df_child_analysis,
  child_age_years,
  response,
  filter_var = (df_child_analysis$item == "change"),
  color_variable = category,
  facet_var = country,
  title_name = "CHANGE"
) + plot_theme(base_family = "Roboto")

change_plot
```

## Save the plots
```{r save-plots}
### Uncomment this if you plan to save the figures!
# fig_output_path <- here::here("outputs/figures/")
# plot_names <-c("born_plot", "internal_plot",
#                 "souls_plot", "change_plot")
# 
# 
# for (name in plot_names){
#   plot_name <- paste0(fig_output_path, "/",name, ".png")
#   
#   #Checks if the exact file name exists in output figures folder and removes it!
#   if(file.exists(plot_name)) {
#     file.remove(plot_name)
#   }
#   
#   #saves the plots in the figures folder!
#   ggsave(get(name), filename = paste0(name, ".png"), 
#          path = fig_output_path,
#          width = 12, height = 8)
# }

```
